---
title: "Pilot Survey"
page-layout: article
---

## Notes from the Team

-   This is the demo of our pilot survey. To access the real survey, please go to <a href="https://pevconjoint.formr.org" target="_blank"><strong>this link</strong></a>.
-   To access the Google sheet of part 1, please go to <a href="https://docs.google.com/spreadsheets/d/1KYjACwzKZ-BmyBlD9X9aIsOgS3F-McoFDdtrPHRd5RI/edit?usp=share_link" target="_blank"><strong>this link</strong></a>.
-   To access the Google sheet of part 2, please go to <a href="https://docs.google.com/spreadsheets/d/1I4EJVDbEbrauo_r1YZWRVML4N8At-BKq3VWpVQmhA-A/edit?usp=share_link" target="_blank"><strong>this link</strong></a>.
-   To access the Google sheet of part 3, please go to <a href="https://docs.google.com/spreadsheets/d/19ELES0Wu7w9kHXI2v5vfo4Q9oYE1kiZgK4MSUWrwA7k/edit?usp=share_link" target="_blank"><strong>this link</strong></a>.
-   In the conjoint part, the attribute of **Guaranteed Range** should be in miles using the `case_when()` function with inputs from the users. Here, since we don't have user inputs, the team chooses to show the percentage instead.

## Welcome Page

Welcome to the survey of **EV Smart Charging**! We are a student team of the George Washington University. In this survey, we want to study the users' willingness to adopt EV smart charging.

This survey will take about **20 minutes** to complete. It can be stopped and picked up at any time. Your personal information will be kept private and won't be shared with anyone else.

This survey consists of:

-   Section 1 - EV ownership questions
-   Section 2 - Smart charging program selections
-   Section 3 - Demographic Questions

If you have any questions, you can reach out to us at [emsepevteam\@gmail.com](mailto:emsepevteam@gmail.com). We will respond at our first convenience.

The survey begins upon clicking the **"Let's Begin"** button below. We greatly appreciate your cooperation!

## Consent Page

To take a part in this survey, you must:

-   Be at least 18 years old.
-   Authorize us to analyze the data exclusively for research purposes.

By clicking on "**I Agree**", you confirm that you have reviewed and understood the information provided in the welcome page and this consent page, and agree to participate in the "Smart Charging Survey".

## Educational Page

Before we start our survey, we want to get you familiarized with EVs and Smart Charging:

-   **EV** is short for Electric Vehicle. A Tesla Model 3 is a typical EV. There are also hybrid EVs (using both electricity and gasoline as power source).
-   **Smart Charging** allows the utility to take control of the EV charging process, including time window and charging amount.

For more information about **Smart Charging**, please watch this **30 seconds video**:

::: {style="width:100%;"}
{{< video https://www.youtube.com/watch?v=TmzksCFVJRA >}} [***Video 1**. Smart Charging Intro* [@evbox2019]]{style="font-size: 0.8em;"}
:::

<br>When you are done reading and watching, please click on the **"Next Page"** button to proceed.

## **Section 1 -** EV Ownership Questions

### Start of Section 1

**1.** Do you own or lease an EV?

-   I own an EV
-   I lease an EV
-   I don't have EV, but plan to buy in the near future
-   No, I don't have an EV

**2.** Which EV do you own/lease/plan/like?

-   We provide a list in alphabetical order to show all EVs available in the USA market, including their makes and models. Please go to our survey for details.

**3.** What is the max range (in miles) of your EV?

-   Below 100
-   100-149
-   150-199
-   200-249
-   250-299
-   300 and Over

**4.** If you charge at **home**, when do you usually charge your car? (Select all that apply)

-   In the Morning (9am \~ 12pm)
-   In the Afternoon (12pm \~ 5pm)
-   In the Evening (5pm \~ 9pm)
-   At Night (9pm \~ 9am)
-   I don't charge at home

**5.** If you charge at **work**, when do you usually charge your car? (Select all that apply)

-   In the Morning (9am \~ 11am)
-   At Noon (11am \~ 1pm)
-   In the Afternoon (1pm \~ 5pm)
-   In the Evening (5pm \~ 9pm)
-   At Night (9pm \~ 9am)
-   I don't charge at work

### **End of Section 1**

Good job! Now we are 1/3 complete! This is the end of **Section 1**.

In **Section 2**:

-   There are **5** questions. Each one provides you with **2** Smart Charging Programs.
-   You need to choose **as if they were your only options** (aka you compare the 2 programs and choose the best one for you).
-   If you are not interested in either of them, you can choose **"I am not interested"**.

We will start with an explanation page and an example question to get you familiarized. Please click on the button below to proceed.

## **Section 2** - Smart Charging Programs

```{r, include=FALSE}
# Read in the choice questions
library(tidyverse)
survey <- read_csv("https://github.com/pingfan0727/Public-Resources/raw/main/datasets/cbc_questions.csv")

# Define the respondent ID
respondentID <- sample(survey$respID, 1)

# Create the subset of rows for that respondent ID
df <- survey %>% 
    filter(respID == respondentID)

# Convert df to json
df_json <- jsonlite::toJSON(df) # Here the df_json is NOT serialized since we are using Kables instead of buttons.
```

### Start of Section 2

Now that we have known basics about your EV ownership and your charging habits, let's move on to Smart Charging program selections!

A Smart Charging program consists of 5 attributes: **Upfront Incentive**, **Free Level 2 Charger**, **Electricity Price Discount**, **Override Window**, and **Guaranteed Range if charged for 8 hrs**.

Here is a brief explanation of each attribute:

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
brief <- tibble(
    `Attribute` = c("Range", "Explanation"),
    `Upfront Incentive:` = c("$100, $300, $500", "It means the amount of money you will be instantly paid if you join the smart charging program. The unit is in USD."),
    `Free Level 2 Charger:` = c("No or Yes", "A \"Yes\" means you will get a free level 2 charger. A level 2 charger enables faster charging than a standard home charger."), 
    `Electricity Price Discount:` = c("10%, 25%, 50%", "If you choose to join this smart charging program, this will be your electricity price discount."), 
    `Override Window:` = c("0.5 ~ 4 hrs", "This is the longest time window per day that you can force override to regular charging, during which time your EV is not controlled by the smart charging program."),
    `Guaranteed Range if charged for 8 hrs:` = c("25%, 50%, 75%", "It means the guranteed range if your car is charged for 8 hrs during smart charging. It shows percentage here, but will be converted to miles."))
row.names(brief) <- NULL

kable(t(brief), escape = FALSE) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  row_spec(row = 1, bold = TRUE)
```

The above table can be accessed via this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>. It's available on top of each question so that you can refer at any time.

The next page provides a sample question to enhance your understanding.

### Section 2 - Sample Question

You are provided with **2 options** of smart charging programs, and an **"I am not interested"** option. You need to treat them **as if they were your only options** and choose the one that you most prefer. You can choose the **"I am not interested"** option if you are not interested in either.

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- tibble(
    `Options:` = c("Option 1", "Option 2"),
    `Upfront Incentive:` = scales::dollar(c(100, 500)),
    `Free Level 2 Charger:` = c("No", "Yes"), 
    `Electricity Price Discount:` = c("25%", "50%"), 
    `Override Window:` = c("0.5 hrs", "4 hrs"),
    `Guaranteed Range if charged for 8 hrs:` = c("100 miles", "300 miles"))

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### **Section 2** - Ready to Start the Questions

The sample question is quite straight-forward. Since **Option 2** has every attribute better than Option 1, I bet you have chosen it.

However, this simplicity is not always the case. There will be trade-offs between the 2 options, and you need to make your own decision. For example, one option might have a large up-front but a low discount, while the other one is the inverse. Then, you need to make decisions based on your preference.

There are **5** choice questions in total. For each question, you have 2 valid options to choose from. Again, you make your choice **as if they were your ONLY options**. If you are really not interested in either of them, you can choose **"I am not interested"**.

Click on **"Next Page"** to proceed.

### Question 1 of 5

(**1 of 5**) If your utility offers you these 2 smart charging programs, which one do you prefer?

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- jsonlite::fromJSON(df_json) %>%
  filter(qID == 1 & altID != 3) %>% 
  mutate(
    altID = paste("Option", altID),
    upfront = scales::dollar(upfront),
    discount = paste0(discount,"%"),
    window = paste(window, "hrs"),
    guaranteed = paste(guaranteed, "%"),
    lv_2_charger_Yes = case_when(lv_2_charger_Yes == 1 ~ "Yes",
                                 lv_2_charger_Yes == 0 ~ "No")) %>%
  select(
    `Options:` = altID,
    `Upfront Incentive:` = upfront,
    `Free Level 2 Charger:` = lv_2_charger_Yes,
    `Electricity Price Discount:` = discount,
    `Override Window:` = window,
    `Guaranteed Range if charged for 8 hrs:` = guaranteed)

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### Question 2 of 5

(**2 of 5**) If your utility offers you these 2 smart charging programs, which one do you prefer?

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- jsonlite::fromJSON(df_json) %>%
  filter(qID == 2 & altID != 3) %>% 
  mutate(
    altID = paste("Option", altID),
    upfront = scales::dollar(upfront),
    discount = paste0(discount,"%"),
    window = paste(window, "hrs"),
    guaranteed = paste(guaranteed, "%"),
    lv_2_charger_Yes = case_when(lv_2_charger_Yes == 1 ~ "Yes",
                                 lv_2_charger_Yes == 0 ~ "No")) %>%
  select(
    `Options:` = altID,
    `Upfront Incentive:` = upfront,
    `Free Level 2 Charger:` = lv_2_charger_Yes,
    `Electricity Price Discount:` = discount,
    `Override Window:` = window,
    `Guaranteed Range if charged for 8 hrs:` = guaranteed)

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### Question 3 of 5

(**3 of 5**) If your utility offers you these 2 smart charging programs, which one do you prefer?

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- jsonlite::fromJSON(df_json) %>%
  filter(qID == 3 & altID != 3) %>% 
  mutate(
    altID = paste("Option", altID),
    upfront = scales::dollar(upfront),
    discount = paste0(discount,"%"),
    window = paste(window, "hrs"),
    guaranteed = paste(guaranteed, "%"),
    lv_2_charger_Yes = case_when(lv_2_charger_Yes == 1 ~ "Yes",
                                 lv_2_charger_Yes == 0 ~ "No")) %>%
  select(
    `Options:` = altID,
    `Upfront Incentive:` = upfront,
    `Free Level 2 Charger:` = lv_2_charger_Yes,
    `Electricity Price Discount:` = discount,
    `Override Window:` = window,
    `Guaranteed Range if charged for 8 hrs:` = guaranteed)

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### Question 4 of 5

(**4 of 5**) If your utility offers you these 2 smart charging programs, which one do you prefer?

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- jsonlite::fromJSON(df_json) %>%
  filter(qID == 4 & altID != 3) %>% 
  mutate(
    altID = paste("Option", altID),
    upfront = scales::dollar(upfront),
    discount = paste0(discount,"%"),
    window = paste(window, "hrs"),
    guaranteed = paste(guaranteed, "%"),
    lv_2_charger_Yes = case_when(lv_2_charger_Yes == 1 ~ "Yes",
                                 lv_2_charger_Yes == 0 ~ "No")) %>%
  select(
    `Options:` = altID,
    `Upfront Incentive:` = upfront,
    `Free Level 2 Charger:` = lv_2_charger_Yes,
    `Electricity Price Discount:` = discount,
    `Override Window:` = window,
    `Guaranteed Range if charged for 8 hrs:` = guaranteed)

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### Question 5 of 5

(**5 of 5**) If your utility offers you these 2 smart charging programs, which one do you prefer?

You can access the attribute table using this <a href="https://pevteam.quarto.pub/attribute-table/" target="_blank"><strong>link</strong></a>.

```{r, echo=FALSE}
library(dplyr)
library(kableExtra)
library(tibble)

alts <- jsonlite::fromJSON(df_json) %>%
  filter(qID == 5 & altID != 3) %>% 
  mutate(
    altID = paste("Option", altID),
    upfront = scales::dollar(upfront),
    discount = paste0(discount,"%"),
    window = paste(window, "hrs"),
    guaranteed = paste(guaranteed, "%"),
    lv_2_charger_Yes = case_when(lv_2_charger_Yes == 1 ~ "Yes",
                                 lv_2_charger_Yes == 0 ~ "No")) %>%
  select(
    `Options:` = altID,
    `Upfront Incentive:` = upfront,
    `Free Level 2 Charger:` = lv_2_charger_Yes,
    `Electricity Price Discount:` = discount,
    `Override Window:` = window,
    `Guaranteed Range if charged for 8 hrs:` = guaranteed)

alts_t <- as.data.frame(t(alts)) %>% 
  rownames_to_column(var = "Attribute")

colnames(alts_t) <- NULL

kable(alts_t, escape = FALSE, align = c('r', 'c', 'c')) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"),
                full_width = FALSE, 
                position = "center") %>%
  column_spec(column = 1, width = '20em') %>%
  column_spec(column = 2, width = '10em') %>%
  column_spec(column = 3, width = '10em') %>%
  row_spec(row = 1, bold = TRUE)
```

-   Option 1
-   Option 2
-   I am not interested

### End of Section 2

Good job! Now we are 2/3 complete! This is the end of **Section 2**.

In **Section 3**:

We will ask about your basic demographic info, and then some other questions including your opinions regarding climate change and commuting preferences.

Please click on the button below to proceed.

## **Section 3** - Demographic Questions

### Start of Section 3

**1.** In what year were you born?

-   A list of years ranging from 1920 to 2005.

**2.** What is your current gender identity?

-   A list of genders.

**3.** You identify your race as (select all that apply):

-   A list of races.

**4.** What is the highest degree or level of school you have completed? (If currently enrolled, please use the highest degree received.)

-   A list of degrees.

**5.** What is your annual household income (from all sources) before taxes and other deductions from pay?

-   A range of income from below \$60,000 to over \$400,000.

**6.** To what extent do you care about the environment and climate change? You may choose from 1 to 5 where:

-   1 being least concerned,
-   5 being most concerned

**7.** Which party did you vote for in the last election?

-   Democratic
-   Republican
-   I didn't vote
-   Prefer not to say

**8.** In what state do you live?

-   A list of states in the USA.
-   An option in the end saying "Outside of USA".

(Optional) If you chose "Outside of USA", please type in your country here:

-   A text input box.

**9.** What is your commute method?

-   On foot
-   By bus
-   By train/subway
-   Self-driving
-   Others

(Optional) If you chose "Others", please specify your commute method here:

-   A text input box.

**10.** How many cars do you have in your household?

-   A list ranging from 0 to over 6.

**11.** Do you have a backup car?

-   Yes, I have one or more backup EV
-   Yes, I have one or more backup gas car
-   Yes, I have both backup EV and gas cars
-   No, I don't have a backup car

### **End of Section 3**

Good job! This is the end of **Section 3**.

Please let us know if you have any other thoughts or feedback on this survey. Your feedback will help us make future improvements :)

-   A big text input box.

## End of Survey

Well done! This is the end of the survey!

Again, if you have any questions, you can reach out to us at [emsepevteam\@gmail.com](mailto:emsepevteam@gmail.com). We will respond at our first convenience.

```{r, include=FALSE}
completion_code <- as.integer(round(runif(1, 10^5, 10^6)))
```

We appreciate your patience and your time. Your completion code is: **`r completion_code`**.
